What is a Selection Coefficient?

### 2021-12-17 graphs_newt_snakes/What_is_sel_coef.Rmd
Figuring out better animations

files <- list.files(path="~/Desktop/data", pattern="byind", full.names=TRUE, recursive=FALSE)
number=7
file <- read.table(files[number], header = TRUE)
file_name <- substr(files[number], 36, 168)
print(paste0("File Name: ", file_name))
```

@@

p1<-ggplot(file[which(file$phenotype<=1001),], aes(phenotype)) + 
  geom_histogram(col = "darkred", fill = "darkred", binwidth=0.05)+ 
  theme_bw()+
  scale_y_log10()+
  xlim(-1, max(file[which(file$phenotype<=1001),]$phenotype)) +
  #ylim(1, 30)+
  # gganimate specific bits:
labs(title = 'Newt Phenotype Dist. Generation: {frame_time}', x = 'Phenotype', y = 'Count') +
  transition_time(gen) +
  ease_aes('linear')
animate(p1, duration = 25, fps = 1, width = 400, height = 400, renderer = gifski_renderer())
anim_save("data/gganimate1.gif")
```

@@

p1<-ggplot(file, aes(fitness)) + 
  geom_histogram(col = "darkred", fill = "darkred", binwidth=0.01)+ 
  theme_bw()+
  xlim(-0.2, 1.0)+
  # gganimate specific bits:
labs(title = 'Newt Fitness Dist. Generation: {frame_time}', x = 'Fitness', y = 'Count') +
  transition_time(gen) +
  ease_aes('linear')
animate(p1, duration = 25, fps = 1, width = 400, height = 400, renderer = gifski_renderer())
anim_save("data/gganimate1.gif")
```

```{r, pheno fit graph, warning = F}
graph_file<-file
title<-"Phenotype by Fitness"
subt<-file_name
    p <- ggplot(graph_file[which(graph_file$phenotype<=1001),], aes(phenotype, fitness)) +
    geom_point(colour = "darkred")+
    ggtitle(title, subtitle = subt) +
    #xlim(-1, 1000) +
    theme_bw() + theme(legend.position="none")+
    # gganimate specific bits:
labs(title = 'Generation: {frame_time}', x = 'Phenotype', y = 'Fitness') +
  transition_time(gen) +
  ease_aes('linear')
animate(p, duration = 25, fps = 1, width = 400, height = 400, renderer = gifski_renderer())
anim_save("data/gganimate1_2.gif")
```

```{r, pheno fit graph log, warning = F}
graph_file<-file
title<-"Phenotype by Fitness"
subt<-file_name
    p <- ggplot(graph_file[which(graph_file$phenotype<=1001),], aes(phenotype, fitness)) +
    geom_point(colour = "darkred")+
    ggtitle(title, subtitle = subt) +
    #xlim(-1, 1000) +
    scale_x_log10()+
    theme_bw() + theme(legend.position="none")+
    # gganimate specific bits:
labs(title = 'Generation: {frame_time}', x = 'Phenotype (log)', y = 'Fitness') +
  transition_time(gen) +
  ease_aes('linear')
animate(p, duration = 25, fps = 1, width = 400, height = 400, renderer = gifski_renderer())
anim_save("data/gganimate1_2log.gif")

>>>>

files <- list.files(path="~/Desktop/data", pattern="byind", full.names=TRUE, recursive=FALSE)
number=1
file <- read.table(files[number], header = TRUE)
file_name <- substr(files[number], 36, 168)
print(paste0("File Name: ", file_name))

@@

p1<-ggplot(file[which(file$phenotype<=1001),], aes(phenotype)) + 
  geom_histogram(col = "darkred", fill = "darkred", binwidth=0.05)+ 
  theme_bw()+
  scale_y_log10()+
  xlim(-1, max(file[which(file$phenotype<=1001),]$phenotype)) +
  #ylim(1, 30)+
  # gganimate specific bits:
labs(title = 'Newt Phenotype Dist. Generation: {frame_time}', x = 'Phenotype', y = 'Count') +
  transition_time(gen) +
  ease_aes('linear')
animate(p1, duration = 30 , fps = round(max(file$gen)/33), width = 400, height = 400, renderer = gifski_renderer())
anim_save("data/gganimate1.gif")
#fps = round(max(file$gen)/33)
```

@@

p1<-ggplot(file, aes(fitness)) + 
  geom_histogram(col = "darkred", fill = "darkred", binwidth=0.01)+ 
  theme_bw()+
  xlim(-0.2, 1.0)+
  # gganimate specific bits:
labs(title = 'Newt Fitness Dist. Generation: {frame_time}', x = 'Fitness', y = 'Count') +
  transition_time(gen) +
  ease_aes('linear')
animate(p1, duration = 30, fps = round(max(file$gen)/33), width = 400, height = 400, renderer = gifski_renderer())
anim_save("data/gganimate1.gif")
```

```{r, pheno fit graph, warning = F}
graph_file<-file
title<-"Phenotype by Fitness"
subt<-file_name
    p <- ggplot(graph_file[which(graph_file$phenotype<=1001),], aes(phenotype, fitness)) +
    geom_point(colour = "darkred")+
    ggtitle(title, subtitle = subt) +
    #xlim(-1, 1000) +
    theme_bw() + theme(legend.position="none")+
    # gganimate specific bits:
labs(title = 'Generation: {frame_time}', x = 'Phenotype', y = 'Fitness') +
  transition_time(gen) +
  ease_aes('linear')
animate(p, duration = 30, fps = round(max(file$gen)/33), width = 400, height = 400, renderer = gifski_renderer())
anim_save("data/gganimate1_2.gif")
```

```{r, pheno fit graph log, warning = F}
graph_file<-file
title<-"Phenotype by Fitness"
subt<-file_name
    p <- ggplot(graph_file[which(graph_file$phenotype<=1001),], aes(phenotype, fitness)) +
    geom_point(colour = "darkred")+
    ggtitle(title, subtitle = subt) +
    #xlim(-1, 1000) +
    scale_x_log10()+
    theme_bw() + theme(legend.position="none")+
    # gganimate specific bits:
labs(title = 'Generation: {frame_time}', x = 'Phenotype (log)', y = 'Fitness') +
  transition_time(gen) +
  ease_aes('linear')
animate(p, duration = 30, fps = round(max(file$gen)/33), width = 400, height = 400, renderer = gifski_renderer())
anim_save("data/gganimate1_2log.gif")
